\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-03-22 paper.tex
Fixed some references

We have chosen to tackle the challenge from several ends: human-aware
navigation and motion planning (\cite{...Mamoun}), situation assessment coupled
with motion planning (\cite{...}), projection of ``mightabilities'' that
anticipates what surrounding agents may do (\cite{Amit...}), and the design and
deployment of a pervasive \emph{knowledge-centric} software architecture.

>>>>

We have chosen to tackle the challenge from several ends: human-aware
navigation and motion planning (\cite{Mainprice2011}), situation assessment
coupled with motion planning (\cite{Mainprice2012}), projection of
``mightabilities'' that anticipates what surrounding agents may do
(\cite{Pandey2011}), and the design and deployment of a pervasive
\emph{knowledge-centric} software architecture.
